SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-05 docs/questioning.tex
addressed some comments mentioned in the telco

@@

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (locus {\sc z}).
Contrary to {\sc sqlg}uard (and other
mechanisms as we sill observe), {\sc sql}check has been
extensively tested in terms of diagnostic performance
as it can be seen in Table~\ref{tab:comp}.
A disadvantage of those mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
framework that partially allows the web
user to specify policies to prevent {\sc xss} attacks.
The key idea behind Noxes is to parse
the {\sc html} that reaches the browser to
find static {\sc url} references. Then, based on
a set of policies Noxes allows or blocks
the request (locus {\sc x}). Such policies
can be also provided by the server (i.e. ``never
follow a link that leads to the malicious.com
web site"). Noxes does not deal with
JavaScript-driven {\sc xss} attacks and it is a rather
simplistic approach.

@@

\section{Analysis}

>>>>

In this section we categorize and describe the various mechanisms
developed to detect the attacks described earlier in
Section~\ref{sec:attacks}. We accompany our descriptions
with comments related to the following dimensions:
a) diagnostic performance, b) security, c) ease of use
and d) detection locus. Regarding the other two
dimensions we provide general remarks in our upcoming
``Analysis" section (\ref{sec:analysis}).

@@

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (locus {\sc z}).
Contrary to {\sc sqlg}uard (and other
mechanisms as we will observe), {\sc sql}check has been
extensively tested in terms of diagnostic performance
as it can be seen in Table~\ref{tab:comp}.
A disadvantage of those mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
framework that partially allows the web
user to specify policies to prevent {\sc xss} attacks.
The key idea behind Noxes is to parse
the {\sc html} that reaches the browser to
find static {\sc url} references. Then, based on
a set of policies Noxes allows or blocks
the request (locus {\sc x}). Such policies
can be also provided by the server (i.e. ``never
follow a link that leads to the malicious.com
web site"). The main issue with Noxes is that
it does not deal with JavaScript-driven {\sc xss}
attacks which is currently the most popular
{\sc xss} attack vector.

@@

\section{Analysis}
\label{sec:analysis}
